Towards Correct Legion

### 2017-08-26 correctnesshpc/paper.tex
fix margins on figure

\begin{figure}
\begin{BVerbatim}
Theorem preservation : forall (e5:e) (t:T) (E:E) (M:M) (L:L) 
(H:H) (S:list (e * e)) (C:list e) (T:T),
    exists v,
      eval M L H S C e5 v E ->
      typing EmptyContext EmptyPriv EmptyConstraint e5 T  ->
      exists G P Omega T, typing G P Omega v T.
\end{BVerbatim}
\caption{preservation theorem}
\label{preservationtheorem}
\end{figure}

\begin{figure}
\begin{BVerbatim}
Theorem progress : forall  (e5:e) (t:T) (M:M) (H:H)  
(C:list e) (T1 T2:T) L (S:list (e * e)),
    typing EmptyContext EmptyPriv EmptyConstraint e5 T1  ->
    (exists E v ,
        is_value v ->
        eval M L H S C e5 v E).
\end{BVerbatim}
\caption{progress theorem}
\label{progresstheorem}
\end{figure}

>>>>

\begin{figure}
\begin{BVerbatim}
Theorem preservation : forall (e5:e) (t:T) (E:E) (M:M) 
(L:L) (H:H) (S:list (e * e)) (C:list e) (T:T),
    exists v,
      eval M L H S C e5 v E ->
      typing NilContext NilPriv NilConstraint e5 T  ->
      exists G P Omega T, typing G P Omega v T.
\end{BVerbatim}
\caption{soundness theorem}
\label{soundnesstheorem}
\end{figure}

\begin{figure}
\begin{BVerbatim}
Theorem progress : forall  (e5:e) (t:T) (M:M) (H:H)  
(C:list e) (T1 T2:T) L (S:list (e * e)),
    typing NilContext NilPriv NilConstraint e5 T1  ->
    (exists E v ,
        is_value v ->
        eval M L H S C e5 v E).
\end{BVerbatim}
\caption{completeness theorem}
\label{completenesstheorem}
\end{figure}
